### 2022-03-15 paper/ase22/experiment.tex
copy n paste

\MyPara{Word Sentiment}
%
we extract sentiments of words using the
\Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
available lexical resource of wrods on Wordnet with three numerical
scores of objectivity, positivity and negativity. Sentiment word
labels from the scores are classified from the algorithm from Mihaela
\etal~\cite{mihaela2017sentiwordnetlabel}.

\MyPara{\Cfg Expansion}
%
We build a reference \Cfg of natural language from the Englush Penn
\Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
The corpus is sampled from 2,499 stories from a tree year \Wsj
collection The \Trb provides a parsed text corpus with annotation of
syntactic and semantic structure. In this experiment We implement the
\trb corpora available through \Nltk, which is a suite of libraries
and programs for \Nlp for english. In addition, we parse the seed
input using into its CFG using the Berkeley Neural
Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
high-accuracy parser with models for 11 languages. The input is a raw
text in natural languge and the output is the string representation of
parse tree. Next after comparing CFGs beteen reference and seed input,
we randomly select 10 expansions for generating templates due to
memory constraint.

\MyPara{Synonyms}
%
\Model searches synosyms of each token from synonym sets extracted
from \Wrdnt using \Spacy open-source library for NLP.

\MyPara{Models}
%
We evaluate the following \sa nmodels via \Model:
\Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
\Dbert~\cite{sanh2019distilbert}. These models are fineturend on \Sstt
and ther accuracies are \BertAcc, \RobertaAcc and \DbertAcc.

\MyPara{Retraining}
%
We retrain \sa models. we split \Model generated test cases into
train/validation/test sets with the ratio of 8:1:1. The number of
epochs and batch_size for retraining are 1 and 16 respectively.

%% For \sa task, input requirements are given for each linguistic
%% capability. Based on the requirements, \Model generates templates and
%% lexicons.
%% \MyPara{Model}
%% \Bert, \Roberta, \Dbert

%% \MyPara{Dataset}
%% reference CFG generation: Treebank corpus
%% word sentiments: sentiwordnet (https://github.com/aesuli/SentiWordNet)
%% cfg parser: berkeley neural parser (https://github.com/nikitakit/self-attentive-parser)
%% synonyms: spacy wordnet synsets (https://spacy.io/universe/project/spacy-wordnet)
%% seed search dataset: stanford sentiment treebank (sst) dataset (https://nlp.stanford.edu/sentiment/)

%% \MyPara{Hyper-Parameter}
%% Number of seed inputs: 10 (random sample)
%% Number of cfg expansions: 10 (random sample)
%% Number of synonyms for a word: 10 (random sample)

%% Besides, we retrain the \sota \sa models aformentioned from test cases
%% generated from \Chlst and \Model. The goal of the retraining is to
%% assess comprehensiveness of test cases according to performance of
%% fine-tuned model. We assume that the comprehensive test cases improve
%% performance of \sa task when fine-tuning with them. On the other hand,
%% fine-tuning models with less comprehensive test cases increases
%% overfitting and decrece model performance.

%% \MyPara{Dataset}
%% Retraining dataset: checklist and our proposed model test cases

%% \MyPara{Hyper-Parameter}
%% Retraining epoach: 1
%% Retraining batch_size: 16

>>>>

\MyPara{Word Sentiment}
%
we extract sentiments of words using the
\Swn~\cite{baccianella2010sentiwordnet}. The \Swn is a publicly
available lexical resource of words on Wordnet with three numerical
scores of objectivity, positivity and negativity. Sentiment word
labels from the scores are classified from the algorithm from Mihaela
\etal~\cite{mihaela2017sentiwordnetlabel}.

\MyPara{\Cfg Expansion}
%
We build a reference \Cfg of natural language from the English Penn
\Trb corpora~\cite{mitchell1993treebank,nltkTreebankCorporaWebPage}.
The corpus is sampled from 2,499 stories from a tree year \Wsj
collection The \Trb provides a parsed text corpus with annotation of
syntactic and semantic structure. In this experiment We implement the
\trb corpora available through \Nltk, which is a suite of libraries
and programs for \Nlp for English. In addition, we parse the seed
input using into its CFG using the Berkeley Neural
Parser~\cite{kitaev2018constituency, kitaev2019multilingual}, a
high-accuracy parser with models for 11 languages. The input is a raw
text in natural language and the output is the string representation of
parse tree. Next after comparing CFGs between reference and seed input,
we randomly select 10 expansions for generating templates due to
memory constraint.

\MyPara{Synonyms}
%
\Model searches synonyms of each token from synonym sets extracted
from \Wrdnt using \Spacy open-source library for NLP.

\MyPara{Models}
%
We evaluate the following \sa models via \Model:
\Bert~\cite{devlin2019bert}, \Roberta~\cite{liu2019roberta} and
\Dbert~\cite{sanh2019distilbert}. These models are fine-tuned on \Sstt
and their accuracies are \BertAcc, \RobertaAcc and \DbertAcc.

\MyPara{Retraining}
%
We retrain \sa models. we split \Model generated test cases into
train/validation/test sets with the ratio of 8:1:1. The number of
epochs and batch size for retraining are 1 and 16 respectively.

### 2022-03-15 paper/ase22/intro.tex
copy n paste

Software testing is the cruicial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, NLP application is a
branch of artifical intelligence software, and testing NLP application
also becomes important process as well.

The prevalent models of NLP are evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy. The accuracy is
a indicator of the performance of the models. Despite its usefulness,
the main limitation of the testing paradigm is that the \ho set often
overestimates the performances. Each dataset comes with specific
biases, and the biases increase the discrepancy of distribution
between dataset and real-world~\cite{recht2019imagenetbias}. The
aforementioned accuracy on \ho set does not consider the discrepancy
and it is limited to achieve comprehensive performrance of the NLP
model. As a consequence, it is difficult to analyze weekness of the
model~\cite{wu2019errudite}.

% this paragraph goes to related, and saying behavioral testing and
% its limitation based on our model's novelty
On the subject of the limitation of traditional testing paradaigm, a
number of methods have been proposed. First, multiple diagnostic
datasets for evaluating NLP model were introduced for obtaning
generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
that, model is evaluated on different aspects such as robustness of
the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.

@@

% our paper's contribution

>>>>

Software testing is the crucial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, NLP application is a
branch of artifical intelligence software, and testing NLP application
also becomes important process as well.

The prevalent models of NLP are evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy. The accuracy is
a indicator of the performance of the models.

Despite its usefulness, the main limitation of the testing paradigm
is that the \ho set often overestimates the performances. Each dataset
comes with specific biases, and the biases increase the discrepancy of
distribution between dataset and
real-world~\cite{recht2019imagenetbias}. The aforementioned accuracy
on \ho set does not consider the discrepancy and it is limited to
achieve comprehensive performrance of the NLP model. As a consequence,
it is difficult to analyze where the errors comes
from~\cite{wu2019errudite}.

On the subject of the limitation of traditional testing paradigm, a
number of methods have been proposed. First, multiple diagnostic
datasets for evaluating NLP model were introduced for obtaining
generalized evaluation of the NLP model~\cite{wang2018glue}. Not only
that, model is evaluated on different aspects such as robustness of
the model on adversarial
sets~\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial},
fairness~\cite{prabhakaran2019fairness,rottger2020hatecheck}, logical
consistancy~\cite{ribeiro2019consistencyeval}, prediction
interpretations~\cite{ribeiroSG16lime} and interactive error
analysis~\cite{wu2019errudite}. Especially, \Chlst implements
behavioral testing methodolgy for evaluating multiple linguistic
capabilities of NLP model~\cite{marcoACL2020checklist}. \Chlst
introduces input-output behaviors of linguistic capabilities and
generates behavior-guided inputs for validating the behaviors. It
provides comprehensive behavioral testing of NLP models through a
number of generated inputs. However, the approach only relies on
manually generated input templates, thus the template generation
becomes expensive and time consuming. In addition, the generated
templates are selective and often too simple, and it is limited to
provide restricted evaluation of linguistic capabilities. Thus, it
does not garauntee the comprehensive evaluation.

@@
